The manageability of pollination networks in an invasion context

### 2017-02-15 paper/draft_2.Rmd
Update title?

---
title: "Biotic invasions fuck with the manageability of pollination networks"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
documentclass: artikel1
bibliography: references.bib
---

>>>>

---
title: "The manageability of pollination networks in an invasion context"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
documentclass: artikel1
bibliography: references.bib
---
